Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-10 minimax.tex
Rephrase to avoid overful

The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile'_1, W'_1)$, depending on the answer. 
Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
We are now faced with the problem of aggregating these values to determine the informative value of the question. Motivated by  \citet{Cailloux2014} we adopt a pessimistic approach, reported to perform better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
However, to avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
Pessimistic considers question $q_1$ to be better  than $q_2$ iff
\begin{align}
	R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2].
\end{align}
%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
%The motivation for using this operator lies in 
In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal $\MMR$.)

>>>>

The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative. 
Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
We now must aggregate these values to determine the informative value of the question. We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff
\begin{align}
	R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2].
\end{align}
%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
%The motivation for using this operator lies in 
In other words if the maximal {\em a posteriori} $\MMR$ of two questions are (nearly) equal, then it considers the (penalized) minimal $\MMR$ values, preferring the question with the lowest value.
(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal $\MMR$ values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal $\MMR$.)
